Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-01 paper.tex
Add to section on static foil coefficient model

@@

>>>>

\subsubsection{Understanding via Static Foil Coefficients}

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of foil coefficient datasets were computed with the XFOIL
viscous panel method code.

The turbine torque coefficient $C_T$ can be related to the blade section
chordwise force coefficient $C_c$ by
\begin{equation}
C_T = \frac{C_c c}{2R} \frac{|U_\mathrm{rel}|^2}{U_\infty^2},
\end{equation}
where the blade section chordwise force (for zero preset pitch)
\begin{equation}
C_c = C_l \sin \alpha - C_d \cos \alpha.
\end{equation}

@@

Note that the common static foil performance metrics fail to show Reynolds
number dependence as close as the max geometric torque coefficient. This means
that the turbine kinematics play an important role, even if the exact dynamics
of the flow are not known.
